---
title: "Week 1 Exercises"
author: "James Buchholz"
date: "May 30, 2022"
output: pdf_document
---

Please complete all exercises below WITHOUT using any libraries/packages.

# Exercise 1
Assign 10 to the variable x. Assign 5 to the variable y. Assign 20 to the variable z.

```{r ex1}

x <- 10
y <- 5
z <- 20

```


# Exercise 2
Show that x is less than z but greater than y.

**Note: your output must be a SINGLE boolean, do not output a boolean for each expression.**

```{r ex2}

if (x < z & x > y) {
  print(T)
}

```

# Exercise 3
Show that x and y do not equal z. 

**Note: your output must be a SINGLE boolean, do not output a boolean for each expression.**

```{r ex3}

if (x != z & y != z) {
  print(T)
}

```


# Exercise 4
Show that the formula `x + 2y = z`. 

**Note: your output must be a SINGLE boolean**

```{r ex4}

a = x + (2 * y)
if (a == z) {
  print(T)
}

```

# Exercise 5
I have created a vector (test_vector) of integers for you. Determine if any of x, y, or z are in the vector. 

**Note: your output must be a SINGLE boolean, do not output a boolean for each expression.**


```{r ex5}
test_vector <- c(1,5,11:22)

if (x %in% test_vector | y %in% test_vector | z %in% test_vector) {
  print(T)
}

```

# Exercise 6
Show which value is contained in the test vector. To do this you will need to create an element-wise logical vector using operators. `x == vector`. Once you have done that you will need to use slicing to return all indices that have matches.
**Note: your output should be two integers**

```{r ex6}

for (i in test_vector) {
  if (i == x %in% test_vector) {
    print(x)
  } 
  if (i == y %in% test_vector) {
    print(y)
  }
  if (i == z %in% test_vector) {
    print(z)
  }
}

```

